### 2015-06-06 doc/manual/resolution.tex
Added convergence scan figure to manual

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{sfincsConvergenceScan.pdf}
\mycaption{Plot generated by \sfincsScanPlot showing a resolution convergence scan for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
\label{fig:convergence}}
\end{center}
\end{figure}

@@

In addition to the 4 resolution parameters above, \sfincsScan~also allows the parameters
\parlink{solverTolerance}, \parlink{xMax}, and \parlink{NxPotentialsPerVth}
to be scanned.  These latter two parameters are not used for the default \parlink{xGridScheme}
so it is usually unnecessary to scan them.  It is also usually unnecessary to scan \parlink{solverTolerance}
since the default value is usually robust.

@@

Typical convergence behavior is illustrated in figure \ref{fig:convergence},
showing the results of \sfincsScan~and \sfincsScanPlot~for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
In this figure, a very large number of values are included for the resolution
parameters, more than you would likely include in routine use of the code.
The red vertical lines emphasize the ``base case'' resolution parameters.
For all parameters scanned, the physical output quantities (particle flux, heat flux, etc)
are essentially unchanged when any of the resolution parameters
are increased beyond the base case value.  Thus, the results in the base case are converged,
and so we can believe the results.
Observe in the figure that the output quantities tend to oscillate when \Nxi~is incremented by 1 and insufficient
\Nxi~is used. Results for even and odd \Nxi~converge to the same value, as one would hope.

If you wish to add more runs to the scan at a later time,
you can alter the relevant \sfincsScan~parameters in the original {\ttfamily input.namelist}~file
and run \sfincsScan~again from the original directory.  The \sfincsScan~code will automatically detect which runs
have already been submitted, so duplicate runs will not be generated.
For example, consider the scan of \Ntheta~described previously in this section,
and suppose you wish to fill in the gaps at \Ntheta = 17 and 21 in the original scan.
To do this, you could set \parlink{NthetaNumRuns} to a large number like 100
and re-run \sfincsScan.  Since \sfincsScan~intelligently avoids duplication,
the only new runs generated will be  \Ntheta = 17 and 21.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{sfincsConvergenceScan.pdf}
\mycaption{Plot generated by \sfincsScanPlot~showing a resolution convergence scan for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
\label{fig:convergence}}
\end{center}
\end{figure}

@@

In addition to the 4 resolution parameters above, \sfincsScan~also allows the parameters
\parlink{solverTolerance}, \parlink{xMax}, and \parlink{NxPotentialsPerVth}
to be scanned.  The last two of these parameters are not used for the default \parlink{xGridScheme}
so it is usually unnecessary to scan them.  It is also usually unnecessary to scan \parlink{solverTolerance}
since the default value is usually robust.

@@

Typical convergence behavior is illustrated in figure \ref{fig:convergence},
showing the results of \sfincsScan~and \sfincsScanPlot~for the example
{\ttfamily geometryScheme4\_2species\_noEr}.
In this figure, a very large number of runs are included in the scan,
more than you would likely include in routine use of the code.
The red vertical lines emphasize the ``base case'' resolution parameters.
For all parameters scanned, the physical output quantities (particle flux, heat flux, etc)
do not visibly change (on the scale of the plots) when any of the resolution parameters
are increased beyond the base case value.  Thus, the results in the base case are well converged,
and so we can believe the results.
Observe in the figure that the output quantities tend to oscillate when \Nxi~is incremented by 1 and insufficient
\Nxi~is used. Results for even and odd \Nxi~converge to the same value, as one would hope.

\begin{figure}
\begin{center}
\includegraphics[width=1.0\textwidth]{sfincsConvergenceScan2.pdf}
\mycaption{Plot generated by \sfincsScanPlot~showing a typical resolution convergence scan for W7-X,
as you might generate during routine use of \sfincs.
\label{fig:convergence2}}
\end{center}
\end{figure}

For routine use of the code, it is not necessary to include as many
runs in the convergence scan as shown in figure \ref{fig:convergence},
and so a more typical routine scan would look like figure \ref{fig:convergence2}.
This scan is for a pure hydrogen plasma in the W7-X standard configuration, using \parlink{rN} = 0.19,
$n_e$ = $10^{20}$ m$^{-3}$, $T_i$ = 3.6 keV, and $T_e$ = 5.5 keV.
Notice the vertical scales in figure \ref{fig:convergence2} have suppressed zeros.
For all of the physical output quantities, the results change by no more than a few percent when each resolution
parameter is increased by 50\%. Hence we can conclude that 
the results are suitably converged at the base case resolution parameters.
The \sfincs~resolution parameters and \sfincsScan~parameters used for this scan were as follows:\\
{\ttfamily
\Ntheta = 19 \\
!ss \parlink{NthetaMinFactor} = 0.7 \\
!ss \parlink{NthetaMaxFactor} = 1.5 \\
!ss \parlink{NthetaNumRuns} = 6 \\
\Nzeta = 125 \\
!ss \parlink{NzetaMinFactor} = 0.7 \\
!ss \parlink{NzetaMaxFactor} = 1.5 \\
!ss \parlink{NzetaNumRuns} = 8 \\
\Nxi = 140 \\
!ss \parlink{NxiMinFactor} = 0.7 \\
!ss \parlink{NxiMaxFactor} = 1.5 \\
!ss \parlink{NxiNumRuns} = 8 \\
\Nx = 5 \\
!ss \parlink{NxMinFactor} = 1 \\
!ss \parlink{NxMaxFactor} = 1.6 \\
!ss \parlink{NxNumRuns} = 4 \\
}
These \sfincsScan~parameters are good for routine convergence tests, although the \sfincs~parameters proper
(\Ntheta, \Nzeta, \Nxi, and \Nx) should be tailored to your application.

If you wish to add more runs to the scan at a later time,
you can alter the relevant \sfincsScan~parameters in the original {\ttfamily input.namelist}~file
and run \sfincsScan~again from the original directory.  The \sfincsScan~code will automatically detect which runs
have already been submitted, so duplicate runs will not be generated.
For example, consider the scan of \Ntheta~described at the start of this section,
and suppose you wish to fill in the gaps at \Ntheta = 17 and 21 in the original scan.
To do this, you could set \parlink{NthetaNumRuns} to a large number like 100
and re-run \sfincsScan.  Since \sfincsScan~intelligently avoids duplication,
the only new runs generated will be  \Ntheta = 17 and 21.

### 2015-06-06 doc/manual/runs.tex
Added convergence scan figure to manual

{\setlength{\parindent}{0cm}
Dimensional quantities in \sfincs~are normalized to ``reference'' values that are denoted by a bar:\\
$\bar{B}$ = reference magnetic field, typically 1 Tesla.\\
$\bar{R}$ = reference length, typically 1 meter.\\
$\bar{n}$ = reference density, typically $10^{19}$ m$^{-3}$, $10^{20}$ m$^{-3}$, or something similar.\\
$\bar{m}$ = reference mass, typically either the mass of hydrogen or deuterium.\\
$\bar{T}$ = reference temperature in energy units, typically 1 eV or 1 keV.\\
$\bar{v} = \sqrt{2 \bar{T} / \bar{m}}$ = thermal speed at the reference temperature and mass\\
$\bar{\Phi}$ = reference electrostatic potential, typically 1 V or 1 kV.\\
}

@@

>>>>

{\setlength{\parindent}{0cm}
Dimensional quantities in \sfincs~are normalized to ``reference'' values that are denoted by a bar:\\
$\bar{B}$ = reference magnetic field, typically 1 Tesla.\\
$\bar{R}$ = reference length, typically 1 meter.\\
$\bar{n}$ = reference density, typically $10^{20}$ m$^{-3}$, $10^{19}$ m$^{-3}$, or something similar.\\
$\bar{m}$ = reference mass, typically either the mass of hydrogen or deuterium.\\
$\bar{T}$ = reference temperature in energy units, typically 1 eV or 1 keV.\\
$\bar{v} = \sqrt{2 \bar{T} / \bar{m}}$ = thermal speed at the reference temperature and mass\\
$\bar{\Phi}$ = reference electrostatic potential, typically 1 V or 1 kV.\\
}

@@

\section{Poloidal and toroidal angles}
